% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\usepackage{hyperref}

\begin{document}

\name{Ghaith Haddad}
% \address used twice to have two lines of address
%\address{123 Sesame street, Sometown, AB}
\address{407.601.9424 - ghaitho@gmail.com}

\begin{resume}

\section{OBJECTIVE}
A challenging position in Technology.

\section{PROFESSIONAL \& EDUCATIONAL EXPERIENCE}

{\sl Sr. Manager, Technology} \hfill        Nov. 2015 - Current  \\
The Walt Disney Company, Orlando, FL \\
  \textit{Park Operations Technology, IoT, Cloud Technologies}
  \begin{itemize} \itemsep -2pt % reduce space between items
      \item Managed the Park Operations Technology team and a Portfolio of 100+ Apps.
      Team responsibilities include building new applications and sustaining
      the current portfolio.
      \item Drove the Park Operations IoT initiative.
      \item Managed Portfolio Rationalization effort to optimize the Park Operations
      Applications.
      \item Played a key role in Disney's effort to reopen the parks after
      COVID shutdown.
      \item Involved in full lifesycle application development, including
      initiation, funding, approval, development, and maintenance.
      \item Managed staffing and internships for the team.
      \end{itemize}

{\sl Manager, Software Development} \hfill        Oct. 2013 - Nov. 2015  \\
Capital One, Wilmington, DE \\
  \textit{Agile, Architecture \& Design, Java, APIs.}
  \begin{itemize} \itemsep -2pt % reduce space between items
      \item Lead Agile teams to deliver bank projects related to Customer
      security \& Small Business systems.
      \item Collaborated with stakeholders and business owners to deliver
       products.
      \item  Managed staffing for Agile teams.
 \end{itemize}

{\sl Manager, Smart Grid Development} \hfill        Jun. 2010 - Sep. 2013  \\
Petra Systems Inc., South Plainfield, NJ \\
  \textit{Java, JavaEE, HBase, Hadoop, Python, C, Zigbee technologies, MS
  Project, Agile Development, ALM.}
  \begin{itemize} \itemsep -2pt % reduce space between items
      \item  Built a high caliber software development team, responsible for
      software and firmware delivery for smart grid and energy
      efficiency applications.
      \item  Architected solutions targeting new products and features and
      supervise the design and implementation phase.
      \item  Participated in writing proposals for funding from different
      government entities.
      \item  Contributed to the company IP by filing patents for new ideas that
      emerged while developing new technologies for Petra Systems.
 \end{itemize}

{\sl Lead Software Engineer} \hfill        Jul. 2008 - May 2010  \\
Petra Systems Inc., South Plainfield, NJ \\
\textit{C, Java, .NET, MySQL, Tomcat, Python, Zigbee technologies.}

{\sl Graduate Research/Teaching Assistant} \hfill   Sep. 2007 - Sep. 2009 \\
University of Central Florida, Orlando, FL \\
\textit{Programming Languages.}

{\sl Graduate Assistant - Research \& Development Engineer} \hfill    Jul. 2006
- Aug. 2007 \\
Institute for Simulation and Training (IST), University of Central Florida,
Orlando, FL \\
\textit{ASP.NET,VB.NET, C\#, MS Access, Windows Mobile 5.0.}

{\sl Research and Development Engineer - Product Team Leader} \hfill   2002 -
2005 \\
Systems and Electronic Development Co. (SEDCO), Amman, Jordan \\
\textit{Oracle, Visual Basic, Visual C++, Rational Tools, MS Project.}

{\sl Research and Development Engineer} \hfill   2001 - 2002 \\
General Center for Software Development (GCESoft), Amman, Jordan \\
\textit{Palm Operating System, C, MS-Access.}

\section{EDUCATION}
{\sl Ph.D.}, Computer Engineering \\
University of Central Florida, Orlando, FL \hfill
Dec 2012 \vspace{0.05in} \\
Research in Java Modeling Language (JML), a behavioral specification language,
and extensible Java compilers. Particularly in developing Timing Analysis
for Safety-Critical Java Systems. Dissertation ``Specification and Runtime
Checking of Timing Constraints in Safety Critical Java''.

{\sl M.Sc.}, Computer Engineering - Digital Systems \\
University of Central Florida, Orlando, FL \hspace{0.2in}  \hfill
May 2007 \vspace{0.05in} \\
Classes include high performance computer architecture, high performance
storage systems, advanced computer security, wireless \& computer networks, FPGA
design and full custom VLSI.

{\sl Bachelor of Science}, Electrical and Computer Engineering \\
Jordan University of Science And Technology, Irbid, Jordan       \hfill    Jan
2001 \vspace{0.05in} \\
GPA 84.2\% (Excellent) \\
Ranked 4 among 121 students graduated in the same academic year, and 1$^{st}$
among semester graduates. Honor-Student Enrollment.

{\sl General Secondary Certificate (Tawjihi)} \\
Irbid Secondary School, Irbid, Jordan \hspace{0.2in}  GPA 94.7\% \hfill
June 1996 \vspace{0.05in} \\
Ranked in top 1\%.

\section{PUBLICATIONS \& PATENTS}
Please view my 20+ publications and patents on my
\href{https://scholar.google.com/citations?user=FdkbqnIAAAAJ&hl=en}{Google Scholar profile}.\\
\url{https://scholar.google.com/citations?user=FdkbqnIAAAAJ&hl=en}

\end{resume}
\end{document}
