% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage{hyperref}

\begin{document}

\name{Ghaith Haddad}
% \address used twice to have two lines of address
%\address{123 Sesame street, Sometown, AB}
\address{407.601.9424 - ghaitho@gmail.com}

\begin{resume}
 
\section{OBJECTIVE}
A challenging position in IT.

\section{PROFESSIONAL \& EDUCATIONAL EXPERIENCE}

{\sl Manager, Software Development} \hfill        Oct. 2013 - Current  \\
Capital One, Wilmington, DE \\
  \textit{Agile, Architecture \& Design, Java, APIs.}
  \begin{itemize} \itemsep -2pt % reduce space between items
      \item  Lead Agile Sprint teams to deliver bank projects for Customer 
      security \& Small Business systems.
      \item  Interacted with stakeholders and business owners to deliver the required product 
      in an Agile environment and per intent.
      \item  Built APIs to integrate with different technologies and platforms across the enterprise as well as third party services.
      \item  Managed staffing for Agile teams.
 \end{itemize}

{\sl Manager, Smart Grid Development} \hfill        Jun. 2010 - Sep. 2013  \\
Petra Solar Inc., South Plainfield, NJ \\
  \textit{Java, JavaEE, HBase, Hadoop, Python, C, Zigbee technologies, MS
  Project, Agile Development, ALM.}
  \begin{itemize} \itemsep -2pt % reduce space between items
      \item  Build a high caliber software development team, responsible for
      delivering software and firmware on the
      smart grid and energy efficiency applications, through taking direct
      responsibility of the development effort or through managing and
      supporting outsourced entities.
      \item  Manage the team efficiently through consistently following best
      practices of application lifecycle management.  Using agile-based
      methodology and team collaboration tools. Manage all project artifacts
      handled by the team (requirements analysis, design, task allocation and
      resource management, software releases, and product maintenance).
      \item  Architect solutions targeting new products and features and
      supervise the design and implementation phase.
      \item  Advise Sales and Marketing on issues related to current products
      or feasibility of ideas and new features requested by customers and
      the marketing team.
      \item  Participate in MRD reviews and deliver advice, suggestions, and
      feasibility information when needed.
      \item  Participate in writing proposals for funding from different
      government entities.
      \item  Build up the company IP by filing patents for new ideas that
      emerged while developing new technologies for Petra.
      \item  Answered to customers inquiries with regards to technical issues,
      provided answers and follow up on issues where appropriate.
      \item  Participate in Standards committees meetings and represent Petra as
      an influential entity on the Standards being developed to support emerging
      technologies.
 \end{itemize}
 
{\sl Lead Software Engineer} \hfill        Jul. 2008 - May 2010  \\
Petra Solar Inc., South Plainfield, NJ \\
\textit{C, Java, .NET, MySQL, Tomcat, Python, Zigbee technologies.}
\begin{itemize} \itemsep -2pt
     \item  Lead communication and software design effort during Petra Solar
     startup.
     \item  Designed and implemented a Zigbee based communication protocol
     between Smart Energy Modules (SEMs) and Data Communicators.
     \item  Designed and implemented an IP based communication protocol between
     Data Communicators in the field and backend servers in order to save and
     track the history of energy generation and manipulate the configuration of
     devices in the field.
     \item  Designed and implemented several software tools to track assembly,
     testing, shipment and RMA for SEMs to ramp up production during the
     company startup period.
     \item  Lead the effort of outsourcing the implementation and testing of
     the final version of the networking software
     \item  Lead the effort of the system level architecture of a Network
     Management System to control and configure customer networks based on
     Petra Solar devices.
     \item  Lead the effort of forming a Software Engineering team in Petra
     Solar
     \item  Lead the effort of integrating Petra Solar network with other
     existing networks and third party devices, by leveraging existing networks
     to act as a backbone for Petra Solar communication, or by leveraging Petra
     Solar Data Communicators to accept third party devices.
\end{itemize} 

{\sl Graduate Research/Teaching Assistant} \hfill   Sep. 2007 - Sep. 2009 \\
University of Central Florida, Orlando, FL \\
\textit{Programming Languages.}
\begin{itemize} \itemsep -2pt
     \item Teaching assistant for the programming languages course.
     \item Research on JML (Java Modeling Language) and extensible Java
     Compilers.
     \item Supervisor - Dr. Gary Leavens.
\end{itemize} 

{\sl Graduate Assistant - Research \& Development Engineer} \hfill    Jul. 2006
- Aug. 2007 \\
Institute for Simulation and Training (IST), University of Central Florida,
Orlando, FL \\ 
\textit{ASP.NET,VB.NET, C\#, MS Access, Windows Mobile 5.0.}
\begin{itemize} \itemsep -2pt
     \item Developed Virtual Check Ride System, a testing system that automates
     the CDL practice test and the virtual walk-around inspection. The system
     provides details reporting about the weaknesses of the examinee and points
     of interest for the examiners. The system interfaces with a simulator and
     collects data resulted from simulated environments and compares it with
     previously collected data to measure the level of profession for drivers.
     \item Developed a work order system on Windows Mobile 5.0.
\end{itemize} 

{\sl Research and Development Engineer - Product Team Leader} \hfill   2002 -
2005 \\
Systems and Electronic Development Co. (SEDCO), Amman, Jordan \\
\textit{Oracle, Visual Basic, Visual C++, Rational Tools, MS Project.}
\begin{itemize} \itemsep -2pt
     \item Developed MediaWorx (Content Management Solution) to international
     clients. Now used by more than 30 different Arabic news agencies and
     newspapers.
     \item Developed FTR (Full Text Retrieval) Engine over MediaWorx (a fast,
     reliable and advanced search engine supporting Arabic language 
     functionality).
     \item Deployed MediaWorx at multiple sites in UAE, KSA and Syria. This
     included installing, training, troubleshooting, and developing
     client-custom features.
     \item Promoted to team leader for Content Management Solutions team
     responsible for analysis, design and development for the communication
     engine for the new products.
\end{itemize} 

{\sl Research and Development Engineer} \hfill   2001 - 2002 \\
General Center for Software Development (GCESoft), Amman, Jordan \\
\textit{Palm Operating System, C, MS-Access.}
\begin{itemize} \itemsep -2pt
     \item Developed a Van Sales system on a Symbol® SPT1700 machine. 
     \item Developed a software module for infrared communication with a
     portable printer for embedded solutions on handheld devices.
     \item Deployed the system on 3 different sites.
\end{itemize} 

{\sl Part-time Lecturer} \hfill   2000 - 2001 \\
Multiple Computer Training Centers, Amman, Jordan \\
\textit{Visual Basic, Web development and design.}
\begin{itemize} \itemsep -2pt
     \item Prepared materials and gave lectures on VB 6 and web development.
\end{itemize} 

{\sl Software Developer} \hfill   1999 - 2000 \\
INFINITYdezign, Irbid, Jordan \\
\textit{Visual Basic, Web development and design.}
\begin{itemize} \itemsep -2pt
     \item Developed DB connectivity and data retrieval for FLASH-based web
     design.
\end{itemize} 

\section{EDUCATION}
{\sl Ph.D.}, Computer Engineering \\
University of Central Florida, Orlando, FL \hfill
Dec 2012 \vspace{0.05in} \\ 
Research in Java Modeling Language (JML), a behavioral specification language,
and extensible Java compilers. Particularly in developing Timing Analysis
for Safety-Critical Java Systems. Dissertation ``Specification and Runtime
Checking of Timing Constraints in Safety Critical Java''.

{\sl M.Sc.}, Computer Engineering - Digital Systems \\
University of Central Florida, Orlando, FL \hspace{0.2in}  \hfill
May 2007 \vspace{0.05in} \\ 
Classes include high performance computer architecture, high performance
storage systems, advanced computer security, wireless \& computer networks, FPGA
design and full custom VLSI.

{\sl Bachelor of Science}, Electrical and Computer Engineering \\ 
Jordan University of Science And Technology, Irbid, Jordan       \hfill    Jan
2001 \vspace{0.05in} \\
GPA 84.2\% (Excellent) \\
Ranked 4 among 121 students graduated in the same academic year, and 1$^{st}$
among semester graduates. Honor-Student Enrollment.

{\sl General Secondary Certificate (Tawjihi)} \\
Irbid Secondary School, Irbid, Jordan \hspace{0.2in}  GPA 94.7\% \hfill
June 1996 \vspace{0.05in} \\  
Ranked in top 1\%.

\section{SOFTWARE \\ PROFICIENCY}
{\sl Programming languages:} Java, J2EE, Python, C,C\#, C++, Visual
Basic 6 and .NET, Perl, Oz. \\
{\sl Database:} HBase, MySQL, ORACLE, MongoDB, MS-Access, SQL Server. \\
{\sl Hardware Design:} Verilog. \\
{\sl Embedded Programming:} Microchip, Freescale, ST. \\
{\sl Internet programming:} Javascript, HTML, Python, AJAX. \\
{\sl Operating systems:} Windows, Linux, Palm OS. \\
{\sl Networks Programming:} TCP/IP, 802.15.4 (Zigbee). \\
{\sl ALM/Agile tools:} Version One, TeamForge, Jira, HPQC, ClearQuest. \\
{\sl Source Control:} Git, SVN, ClearCase, CVS. \\
{\sl Object Oriented Design:} UML, MS Visio, Rational Rose, RequisitePro. \\
{\sl Project Management:} MS Project, TeamForge.

\section{PUBLICATIONS}
\begin{itemize} \itemsep -2pt
     \item Alatrash, H.; Mensah, A.; Mark, E.; Haddad, G.; Enslin, J.; ,
     ``Generator Emulation Controls for Photovoltaic Inverters,'' Smart Grid,
     IEEE Transactions on , vol.3, no.2, pp.996-1011, June 2012 doi:
     10.1109/TSG.2012.2188916, URL:
     http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=6198747
     \item Ghaith Haddad and Gary T. Leavens. ``Specifying subtypes in SCJ
     programs.'' To appear in Concurrency and Computation Practice and Experience,
     John Wiley \& Sons, Ltd., online October 4, 2012 at
     http://dx.doi.org/10.1002/cpe.2930.
     \item Ghaith Haddad and Gary T. Leavens. ``Specifying subtypes in SCJ
     programs.'' In Proceedings of the 9th International Workshop on Java
     Technologies for Real-Time and Embedded Systems(JTRES '11). ACM, New York,
     NY, USA, 40-46. DOI=10.1145/2043910.2043917
     http://doi.acm.org/10.1145/2043910.2043917
     \item Ghaith Haddad, Faraz Hussain, and Gary T. Leavens. ``The Design of
     SafeJML, a Specification Language for SCJ with Support for WCET
     Specification.'' In JTRES '10: Proceedings of the 8th International Workshop
     on Java Technologies for Real-Time and Embedded Systems, Prague, August
     2010, pages 155-163.
     Also Dept. of Electrical Engineering and Computer Science, University of
     Central Florida, CS-TR-10-06, June 2010.
     \item Kalibera, T., Parizek, P., Haddad, G., Leavens, G. T., and Vitek, J.
     2010. ``Challenge benchmarks for verification of real-time programs.'' In
     Proceedings of the 4th ACM SIGPLAN Workshop on Programming Languages Meets
     Program Verification(Madrid, Spain, January 19 - 19, 2010). PLPV '10. ACM,
     New York, NY, 57-62. DOI= http://doi.acm.org/10.1145/1707790.1707800
     \item Ghaith Haddad and Gary T. Leavens. ``Extensible Dynamic Analysis for
     JML: A Case Study with Loop Annotations.'' Dept. of Electrical Engineering
     and Computer Science, University of Central Florida, CS-TR-08-05, April
     2008.
     \item Ghaith Haddad, Gustavo Gamboa and Issa Batarseh, ``Interactive
     Electrical Circuit Tutoring Tool - eTutor.'' ASEE-SE 2008, April 2008
     \item G. Haddad, B. Horine, and L. B\"{o}l\"{o}ni. ``UCFTAC: A
     Control Based Supply Chain Management Trading Agent.'' In The 20th
     International FLAIRS Conference, May 2007
     \item G. Haddad and D. Turgut. ``DSASim: A simulation
     framework for dynamic spectrum allocation.'' Proceedings of IEEE Wireless
     Communications and Networking Conference (WCNC), March 2007.
\end{itemize} 

\section{PATENTS}
\begin{itemize} \itemsep -2pt
     \item Haddad, G. 2011. ''Mesh Network Fragmented Upgrade Method.''
     Publication Number WO2013006690, PCT Application Patent No. 
     PCT/US2012/045532, filed July 5, 2012 and published May 8, 2014. 
     \item Batarseh, I., Shoubaki, I., Harb, S., Haddad, G. 2012. ''Sybmolic
     Switch/Linear Circuit Simulator(SymCir).'' U.S. Patent 8,219,374, filed 
     February 21, 2008, and issued July 10, 2012.
     \item Batarseh, I., Haddad, G., Oreifej, R., Al-Haddad, R. 2013
     ''Interactive Electronic Book Operating Systems and Methods.''
     U.S. Patent 8,352,876, filed February 21, 2008, and issued January 8,
     2012.
\end{itemize} 

\section{CONTINUING EDUCATION CLASSES}
\begin{itemize} \itemsep -2pt
     \item Inclusive Leadership, Capital One, Nov 2015.
     \item Behavioral Interviewing, Capital One, Mar 2015.
     \item Creative Decision Making and Problem Solving, Capital One, Feb 2015.
     \item Scaled Agile Framework (SAFe), Capital One, Jan 2015.
     \item Agile: SAFe Product Manager/Product Owner, Capital One, Jan 2015.
     \item Essentials of Management, Petra Solar, Oct-Nov 2011.
     \item Managing within the Law, Petra Solar, June 3rd 2010.
     \item Low-Power Product Design Seminar, Freescale, April 15, 2009.
     \item Foundation of Modeling and Simulation, University of Central
     Florida, Division of Continuing Education, June 2006.
     \item Building High Performance Teams Training Seminar, AMIDEAST, April
     2005.
     \item MS VB.NET, CompuBase, August 2002.
     \item CISCO Networking Academy Program, Jordan University of Science and
     Technology, Nov. 2000 - June 2001.
     \item ORACLE Developer, Mansi Technology Center, Dec. 2000.
     \item ORACLE DBA, Mansi Technology Center, April 2001.
\end{itemize} 

\section{PROJECTS OF INTEREST}

{\sl Single Sign On (SSO) for Capital One Direct Bank Customers} \hfill   2014 \\
\begin{itemize} \itemsep -2pt
     \item Provide Direct Bank customers with a single sign on experience 
            that supports other lines of business.
     \item Siggnificant customer impact (7M+).
     \item Led an Agile team to develop the UX.
     \item Front-end integrated with a handful of back-end systems through APIs.
\end{itemize} 

{\sl PSE\&G Pole-Mount distributed solar and two-way communication} \hfill   2009-2012 \\
\begin{itemize} \itemsep -2pt
     \item Largest Distributed Solar Energy project at the time (\$200M).
     \item Lead a software development team and managed an outsourced team 
            to develop two-way end to end communication and a backend solution with 
            a front-end customer-facing full UX.
\end{itemize} 

{\sl eBOS - the eBook Operating System} \hfill   2007 \\
\begin{itemize} \itemsep -2pt
     \item An electronic book that includes many helpful features for students.
     \item Developed in Java.
     \item Supervisor: Dr. Issa Batarseh, Director of Electrical Engineering \&
     Computer Science - batarseh@mail.ucf.edu.
     \item U.S. Patent 8,352,876.
\end{itemize} 

{\sl eTutor - Interactive Electrical Circuits Tutoring Tool} \hfill   2007 \\
\begin{itemize} \itemsep -2pt
     \item A symbolic analysis tool that interactively tutors students how to
     solve electrical circuits problems by analyzing their input and providing
     feedback on the errors committed by the student
     \item Developed in Java.
     \item Supervisor: Dr. Issa Batarseh, Director of Electrical Engineering \&
     Computer Science - batarseh@mail.ucf.edu.
\end{itemize} 

{\sl Symbolic Circuits Solver } \hfill   2006 \\
\begin{itemize} \itemsep -2pt
     \item A non-simulation package for extracting symbolic equations from
      Netlists and generating a closed-form solution for electrical circuits.
     \item Developed using Java.
     \item Supervisor: Dr. Issa Batarseh, Director of Electrical Engineering \&
     Computer Science - batarseh@mail.ucf.edu.
\end{itemize} 

{\sl Introduction to Electrical Circuits Website} \hfill   2006 \\
\begin{itemize} \itemsep -2pt
     \item Intended to help students gain basic concepts of circuit analysis and
     applications.
     \item Developed by a team of faculty and students at UCF, using
     HTML and VB.NET – http://www.ecircuits.cecs.ucf.edu
     \item Supervisor: Dr. Issa Batarseh, Director of Electrical
     Engineering \& Computer Science - batarseh@mail.ucf.edu. Project Manager:
     Dr. Jaber Abu Qahouq, jaberq@ieee.org
\end{itemize} 

{\sl Marathon Results Manager} \hfill   2002 \\
\begin{itemize} \itemsep -2pt
     \item Developed for Dead Sea Ultra Marathon www.deadseamarathon.com and
     used since 2002.
     \item A comprehensive system, using SymbolTM SPT 1800 running Palm OS with
     embedded barcode reader. The system can collect data for Start, Stations,
     and arrival and generate results reports and certificates for the runners
     based on runner category and run type.
     \item Implemented in C (Palm OS) and MS Access.
\end{itemize} 

{\sl Arabic Root Extractor} \hfill   2001 \\
\begin{itemize} \itemsep -2pt
     \item An intelligent Arabic root-extraction engine, implemented in C++, as
     part of an Arabic language analysis system. Consists of three phases:
     Arabic lexical analysis, word tokenizing, and root extraction.
     \item Graduation project. Rated as one of the best graduation projects
     presented.
     \item Supervisor, Dr. Taisir Eldos. Team members, Eng. Khalid Ajlouny.
\end{itemize} 

{\sl Irbid Municipality Website} \hfill   2000 \\
\begin{itemize} \itemsep -2pt
     \item The official site for Irbid, Jordan. URL: www.irbid.gov.jo.
     Contains extensive information about Jordan, and Irbid, a historical
     overview for the municipality, and services provided by the municipality
     to the community.
     \item The website was designed by INFINITYdezign.
     \item Implemented the server-side scripts. A guest book, a search engine,
     a feedback form. All written in \textit{Perl}.
\end{itemize} 

{\sl Arabic Version Website, The Special Program for Food Security - SPFS - FAO}
\hfill   1997 \\
\begin{itemize} \itemsep -2pt
     \item Designed using HTML. URL: www.fao.org/spfs
     \item Supervisor, Prof. Bassam Snobar.
\end{itemize} 

\section{PROFESSIONAL AFFILIATIONS}
\begin{itemize} \itemsep -2pt
     \item IEEE UCF Student Chapter - Treasurer/VP for SECON2007/ SECON2008
     \item IEEE Orlando Section  - Computer Society Chapter Chair (2007-2009)
     \item IEEE - since 1997.
     \item IEEE Computer Society.
     \item ACM - since 2007.
\end{itemize} 

\section{OTHER INTERESTS}
\begin{itemize} \itemsep -2pt
     \item Institute for Simulation and Training Booth Assistance - IITSEC 2006
     \item International office assistance - IITSEC 2005.
     \item Worked on a charity's staff for the Dead Sea Ultra Marathon, as a
     results manager for all events that took place 2002-2005.
     \item Playing music and singing.
\end{itemize} 


\end{resume}
\end{document}




